Outbreak response models of vaccine-preventable diseases in humans (1970-2019) - A systematic review (Supplementary Files)

### 2023-04-23 analyses/scripts/orv_sys_rev_supplementary.Rmd
Updated some paths

```{r echo=FALSE, include=FALSE}
# Load the cleaned data 
long_data <- read_rds('../data/final_data/cleaned_data/review_data_long_cleaned.rds')

#The cleaned data without citations
compact_data_init <- read_rds('../data/final_data/cleaned_data/review_data_compact_cleaned.rds')

@@

# The data with citations 
compact_data_with_citation_keys_init <- read_rds(normalizePath('../data/final_data/cleaned_data/compact_data_with_citation_keys_cleaned.rds'))

>>>>

```{r echo=FALSE, include=FALSE}
# Load the cleaned data 
long_data <- read_rds('../data/review_data_long_cleaned.rds')

#The cleaned data without citations
compact_data_init <- read_rds('../data/review_data_compact_cleaned.rds')

@@

# The data with citations 
compact_data_with_citation_keys_init <- read_rds(normalizePath('../data/compact_data_with_citation_keys_cleaned.rds'))
